---
title: "Regression and Statistical Inference"
---

# Assignment

------------------------------------------------

### Task 1:

Reading the data for its dimensions,

```{r}
# Loading the file car_prices
df_car_prices <- readRDS("../../Causal_Data_Science_Data/car_prices.rds")
# Dimensions of the data
dim(df_car_prices)
```
The data has `181 rows` and `22 columns`.

### Task 2:

> Detailed look of the data

```{r}
#| warning: false
t(summary(df_car_prices))
```

>Correlation of numerical columns

```{r}
# Selecting only numeric columns
numeric_cols <- df_car_prices[sapply(df_car_prices, is.numeric)]

# Calculating correlation matrix
cor(numeric_cols)
```

> Data types of each column and the samples 

```{r}
# Data Types
str(df_car_prices)
```
Total unique data types in the car_price data set
```{r}
# Seeing the datatypes in the data
column_types <- sapply(df_car_prices, class)
# Get unique data types
unique_types <- unique(column_types)
# Print the unique data types
print(unique_types)
```

There are 2 types of data types in the : character and numeric.

The `numeric` data type include both *integers and decimals* whereas `character` data types represent *text or strings*.

### Task 3:

```{r}
lm_model <- lm(price ~ ., data = df_car_prices)
summary(lm_model)
```

The significance of the parameters impacting the car price is denoted by the number of asterisks (*). The statistical significance for the mentioned columns is exceptionally low, indicating a high level of significance.

* *enginetypeohc*

* *enginetypeohcv*

* *cylindernumberfive*

* *cylindernumberfour*

* *enginesize*

* *stroke*

* *peakrpm*

### Task 4:

Choice of the Regressor: `enginesize`

* *Data type*: As observed in the linear regression summary, the `enginesize` variable is of `numeric` data type, accommodating both integer and decimal values. In this data set, it is notable for having integer values such as 130 152 109, etc.

* *Effect on Price:* The coefficient of the `enginesiz` is 125.934. This value indicates that for each unit increase in size, the price is expected to increase by 125.934 units, keeping other variable constants.

* *Statistical Significance*: The p-value for `enginesize`, which stands at `5 × 10^-6^`, is notably small. This suggests a high level of significance, indicating a substantial effect on the Price.


### Task 5:

```{r}
#| warning: false
library(dplyr)
df_car_prices_upd <- mutate(df_car_prices, seat_heating = TRUE)
lm_model_sh <- lm(price ~ . + seat_heating, data = df_car_prices_upd)
```

> Summary of the new model to see the coefficient of 'seat_heating'

```{r}
#| warning: false
summary(lm_model_sh)
```
From the table, it's evident that the variable seat_heating exhibits no significant impact on the price. The regression model fails to establish any correlation between the price and seat_heating, resulting in a coefficient marked as NA (Not Available). This absence of correlation may be attributed to the phenomenon known as `Multi-Collinearity`. In this case, the seat_heating variable is consistently set to `True` without any variation, rendering the model incapable of estimating a coefficient for it.