---
title: "Causality"
---

# Assignment

------------------------------------------------------------------------

### Example of number of facebook friends with average grade in university course

```{r}
#| warning: false
#| include: false
library(ggplot2)
library(dplyr)
```

> Generating data

```{r}
# Generating few data points
students <- seq(1, 100, by = 1)

facebook_friends <- rnorm(length(students), mean = 300, sd = 100) + 
  rnorm(length(students), mean = 0, sd = 30)  # noise

average_grade <- rnorm(length(students), mean = 70, sd = 10) + 
  0.5 * facebook_friends + 
  rnorm(length(students), mean = 0, sd = 10)  # noise

# Creating a data frame
data <- data.frame(Student_ID = students, 
                   Facebook_Friends = facebook_friends,
                   Average_Grade = average_grade)
head(data)
```

>ggplot()

```{r}
# Scatter Plot
ggplot(data, aes(x = Facebook_Friends, y = Average_Grade)) +
  geom_point() +
  labs(title = "Spurious Correlation: Facebook Friends vs. Average Grade",
       x = "Number of Facebook Friends",
       y = "Average Grade in University Courses")
```
> Correlation

```{r}
# Calculate the correlation coefficient
correlation_coefficient <- cor(data$Facebook_Friends, data$Average_Grade)
paste("Correlation coefficient: ", correlation_coefficient)
```

::: callout-note
Line Chart that shows a positive correlation between Facebook Friends and Average Grade. The correlation coefficient is `>0.9`, which indicates a strong positive correlation.
:::

Correlation doesn't imply causation. In my generated example, I deliberately created a scenario to illustrate the concept of spurious correlation without asserting any causal link between the number of Facebook friends and academic performance.

In reality, there could be numerous factors influencing academic performance, and the number of Facebook friends is unlikely to be a direct cause. Some real-world factors that may contribute to good grades include:

* *Study Habits:* Students who develop effective study habits are likely to perform better academically.

* *Attendance:* Regular attendance in classes and engagement with course materials can positively impact grades.

* *Interest in the Subject:* Genuine interest in the subject matter often leads to better understanding and performance.

* *Time Management:* Efficient time management is crucial for balancing academic and extracurricular activities.
