---
title: "Directed Acyclic Graphs"
---

# Assignment

------------------------------------------------------------------------

### Task 1:

```{r}
library(tidyverse)
library(dagitty)
library(ggdag)
library(ggplot2)

dag <- 'dag {
bb="0,0,1,1"
Parking [exposure,pos="0.1,0.5"]
Sales [outcome,pos="0.5,0.5"]
Location [pos="0.5,1"]
Parking -> Sales
Location -> Parking
Location -> Sales
}
'
ggdag_status(dag) +
theme_dag() +
theme(plot.background = element_rect(fill = "lightblue"))
```

### Task 2:

> Loading the customer_sat data set

```{r}
df_customer_sat <- readRDS("../../Causal_Data_Science_Data/customer_sat.rds")
head(df_customer_sat)
```

#### 1.   Regress `satisfaction` on `follow_ups`

```{r}
lm_model1 <- lm(satisfaction ~ follow_ups, data = df_customer_sat)
```
> Summary

```{r}
summary(lm_model1)
```

#### 2.   Regress `satisfaction` on `follow_ups` and account for `subscription`

```{r}
lm_model_2 <- lm(satisfaction ~ follow_ups + subscription, data = df_customer_sat)
```
> Summary

```{r}
summary(lm_model_2)
```


### Task 3:

* Common Predictors:

  + Both models include an intercept and the predictor variable follow_ups.
  + The coefficient for follow_ups is negative in Model 1 and positive in Model 2.

* Additional Predictors in Model 2:

 + Model 2 includes two additional predictor variables: subscriptionPremium and subscriptionPremium+.
 + These variables have positive coefficients, indicating a positive impact on the dependent variable.

* Possible Explanation:

  + The introduction of subscription-related predictors (subscriptionPremium and subscriptionPremium+) in Model 2 might be associated with a change in the business strategy or customer segmentation.
  + The positive coefficients for subscription-related predictors in Model 2 suggest that having a premium subscription or a premium+ subscription is associated with higher values of the dependent variable.

* Overall Model Performance:

  + Model 2 has a higher adjusted R-squared (0.9487) compared to Model 1 (0.6316), indicating that the predictors in Model 2 explain a larger proportion of the variance in the dependent variable.

* Statistical Significance:

  + All coefficients in Model 2, including the intercept, follow_ups, and subscription-related predictors, are statistically significant.
  
::: callout-note
In summary, the differences in coefficients between the two models can be attributed to the introduction of new predictors related to subscription types in Model 2. The positive coefficients for subscription-related predictors suggest that these subscriptions contribute significantly to the higher values of the dependent variable in the presence of follow-ups.
:::

### Task 4

> Without Conditioning on Subscription

```{r}
simps_not_cond  <- ggplot(df_customer_sat, aes(x = follow_ups, y = satisfaction)) +
  geom_point(alpha = .8) +
  stat_smooth(method = "lm", se = F)

simps_not_cond
```

> Conditioning on Subscription

```{r}
simps_cond <- ggplot(df_customer_sat, aes(x = follow_ups, y = satisfaction, color = subscription )) +
  geom_point(alpha = .8) +
  stat_smooth(method = "lm", se = F) +
  theme(legend.position = "right")

simps_cond 
```