---
title: "Randomized Controlled Trials"
---

# Assignment

------------------------------------------------------------------------

> Loading the data set abtest_online

```{r}
df_abtest_online  <- readRDS("../../Causal_Data_Science_Data/abtest_online.rds")
df_abtest_online
```

### Task 1:

Plotting the covariates to check the balance across the groups

* *Treatment Group*: chatbot = `TRUE`

* *Control Group*: chatbot = `FALSE`

```{r}
#| warning: false
library(tidyverse)

df_abtest_online %>% 
  group_by(chatbot) %>% 
  summarise(mean_outcome = mean(purchase_amount))
```
::: callout-note
The average outcome of the non-chatbot group is higher.
:::

```{r}
library(ggplot2)

compare_purchase_amount <- 
  ggplot(df_abtest_online, 
         aes(x = chatbot, 
             y = purchase_amount, 
             color = as.factor(chatbot))) +
  stat_summary(geom = "errorbar", 
               width = .5,
               fun.data = "mean_se", 
               fun.args = list(mult=1.96),
               show.legend = F) +
  labs(x = NULL, y = "purchase_amount", title = "Difference in purchase amount")
```

> Plot with outcome purchase amount

```{r}
compare_purchase_amount
```
> The above two plots with outcome represents covariate balance between the two groups.

### Task 2:

```{r}
lm_sales_ate <- lm(purchase_amount ~ chatbot, data = df_abtest_online)
summary(lm_sales_ate)
```
> The variable chatbot appears to exert a `negative` influence on the purchase amount. This suggests that the presence of the chatbot has led to a decline in sales, consequently reducing the purchase amount.

### Task 3:

> Subgroup-Specific effects by including an interaction

```{r}
lm_cate1 <- lm(purchase_amount ~ chatbot * mobile_device, data = df_abtest_online)

lm_cate2 <- lm(purchase_amount ~ chatbot * previous_visit, data = df_abtest_online)

lm_cate3 <- lm(purchase_amount ~ chatbot * mobile_device + previous_visit, data = df_abtest_online)

lm_cate4 <- lm(purchase_amount ~ chatbot * mobile_device + chatbot * previous_visit, data = df_abtest_online)
```

> Summary for lm_cate4 : The R^2^ value for `lm_cate4` is highest among above 4 interaction

```{r}
summary(lm_cate4)
```

### Task 4:

```{r}
lm_binary <- glm(purchase ~ chatbot * mobile_device + chatbot * previous_visit, family = binomial(link = 'logit'), data = df_abtest_online)
summary(lm_binary)
```
### Interpretation of Coefficient:

The coefficient in the logistic regression output represents the log-odds of making a purchase when a particular variable is present compared to when it's not. However, these coefficients are not as intuitively interpretative as in linear regression.

* To interpret the coefficient:

  + If the coefficient is positive, it suggests an increase in the log-odds of making a purchase when the chatbot is present.
  
  + If the coefficient is negative, it suggests a decrease in the log-odds of making a purchase when the chatbot is present.
  
* Odds Ratio:

  + The exponentiated coefficient gives the odds ratio. If the odds ratio is greater than 1, it implies an increase in the odds of making a purchase. If it's less than 1, it implies a decrease.

  + For example, if the odds ratio is 1.5, it means the odds of making a purchase are 50% higher when the chatbot is present compared to when it's not.

::: callout-note
In summary, the logistic regression helps understand how the presence of the variables influences the likelihood of a customer making a purchase. The coefficient and odds ratio provide insights into the direction and magnitude of this influence.
:::