---
title: "Difference-in-Differences"
---

# Assignment

------------------------------------------------------------------------

> Loading the data set hospdd

```{r}
#| warning: false
library(dplyr)

df_hospdd  <- readRDS("../../Causal_Data_Science_Data/hospdd.rds")
head(df_hospdd)
```

> Hospitals in which the new admission procedure was implemented

```{r}
treatment_hospital <- df_hospdd %>%
  group_by(hospital) %>%
  summarise(procedure_count = sum(procedure))

treatment_hospital
```
The above Table shows that out of 46 hospitals, hospitals with label 1 to 18 had the new admission procedure whereas the hospitals with label 19 to 46 had the old admission procedure.

> Months in which the new admission procedure was implemented

```{r}
treatment_month <- df_hospdd %>%
  group_by(month) %>%
  summarise(procedure_count = sum(procedure))

treatment_month
```

The above Table shows that out of 7 months, months with label 4,5,6 and 7 had the new admission procedure whereas the months with label 1,2 and 3 had the old admission procedure.

::: callout-note

* Treatment variable = procedure
* Before Treatment:
  + Treatment Group: 18 hospitals before month 4
  + Control Group: 28 hospitals before month 4
* After Treatment:
  + Treatment Group: 18 hospitals from month 4
  + Control Group: 28 hospitals from month 4
  
:::

```{r}
treatment_hospital <- df_hospdd %>%
  group_by(hospital, month) %>%
  summarise(procedure_count = sum(procedure), .groups = 'drop')

treatment_hospital
```

### Task 1:

> Mean satisfaction for treated and control hospitals before and after the treatment

```{r}
# Step 1: Subset the data for treatment and control hospitals
treated_hospitals <- df_hospdd %>% filter(procedure == 1)
control_hospitals <- df_hospdd %>% filter(procedure == 0)

# Step 2: Compute mean satisfaction for treated hospitals before and after treatment
mean_satis_before_treated <- treated_hospitals %>%
  filter(month < 4) %>%
  pull(satis) %>%
  mean(na.rm = TRUE)
mean_satis_before_treated = 0

mean_satis_after_treated <- treated_hospitals %>%
  filter(month >= 4) %>%
  pull(satis) %>%
  mean(na.rm = TRUE)

# Step 3: Compute mean satisfaction for control hospitals before and after treatment
mean_satis_before_control <- control_hospitals %>%
  filter(month < 4) %>%
  pull(satis) %>%
  mean(na.rm = TRUE)

mean_satis_after_control <- control_hospitals %>%
  filter(month >= 4) %>%
  pull(satis) %>%
  mean(na.rm = TRUE)

# Step 4: Print the results
cat("Mean Satisfaction - Before (Treated):", mean_satis_before_treated, "\n")
cat("Mean Satisfaction - After (Treated):", mean_satis_after_treated, "\n")
cat("Mean Satisfaction - Before (Control):", mean_satis_before_control, "\n")
cat("Mean Satisfaction - After (Control):", mean_satis_after_control, "\n")
```

> DiD

```{r}
diff_before_treatment = mean_satis_before_treated - mean_satis_before_control
diff_after_treatment = mean_satis_after_treated - mean_satis_after_control

did_estimate <- diff_after_treatment - diff_before_treatment
did_estimate
```

### Task 2:

* month + hospital

```{r}
model1<- lm(satis ~ month + hospital, data = df_hospdd)
model1
```
* as.factor(month) + as.factor(hospital)

```{r}
model2 <- lm(satis ~ as.factor(month) + as.factor(hospital), data = df_hospdd)
model2
```

>Interpretation:

* Model 1 assumes that month and hospital are numeric variables, and it models a linear relationship between these numeric variables and satis.

* Model 2 treats month and hospital as factors (categorical variables), and it models the categorical effects of each level of month and hospital on satis.