---
title: "Instrumental Variables"
---

# Assignment 

------------------------------------------------------------------------

> Loading data set rand_enc

```{r}
df_rand_enc <- readRDS("../../Causal_Data_Science_Data/rand_enc.rds")
df_rand_enc
```

### Task 1:

```{r}
dag <- dagify(
  Y ~ D,
  Y ~ U,
  D ~ U,
  D ~ Z,
  exposure = "D",
  latent = "U",
  outcome = "Y",
  coords = list(x = c(U = 1, D = 0, Y = 2, Z = -1),
                y = c(U = 1, D = 0, Y = 0, Z = 0)),
  labels = c("D" = "Pop-up Feature", 
             "Y" = "App Usage", 
             "U" = "Unobserved Factor",
             "Z" = "Encouragement")
)
ggdag(dag, text = T) +
  theme_dag() +
  theme(plot.background = element_rect(fill = "lightblue"))
```

### Task 2:

```{r}
model_biased <- lm(time_spent ~ used_ftr, data = df_rand_enc)
summary(model_biased)
```

### Task 3:

```{r}
cor(df_rand_enc)
```
> Correlation Analysis:

* The correlation between rand_enc and used_ftr is 0.204, indicating a weak positive correlation.
* The correlation between used_ftr and time_spent is 0.705, indicating a moderate to strong positive correlation.
* The correlation between rand_enc and time_spent is 0.130, indicating a weak positive correlation.

> Overall Assessment:

* The correlations between the randomly selected customer and other variables appear weak.
* This indicates potential endogeneity issues.
* Instrumental variable estimation can be employed to mitigate bias in such cases.
* Unobserved factors may impact both the utilized features and the time spent.
* Instrumental variable estimation becomes useful in addressing omitted variable bias under these circumstances.
* This approach helps account for unobserved variables, enhancing the robustness of the analysis.
* A valid instrumental variable for estimation should be relevant and exhibit no direct correlation with the outcome variable(time_spent), except through its association with the features.

### Task 4:

```{r}
library(estimatr)

model_iv <- iv_robust(time_spent ~ used_ftr | rand_enc, data = df_rand_enc)
summary(model_iv)
```
* The initial estimate is 10.82, while the IV estimate is slightly lower at 9.73.
* The initial estimate, often termed the naive estimate, tends to be higher.
* The IV estimate (9.73) corrects for hidden factors associated with encouragement.
* It provides a more precise estimate by accounting for these concealed factors, resulting in a slightly lower value.
* Unlike the naive estimate, which includes both the impact of feature usage and the influence of encouragement, the IV estimate isolates the effect of feature usage.
* This isolation leads to a more accurate depiction of the impact of feature usage on app time spent.